Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-29 manuscript/draft.Rmd
add hindcasting notes

To evaluate the expected accuracy and uncertainty of forecasts assess the
performance of these forecasts within existing time-series data. [[citaton?]]

>>>>

Evalutating a models predictive performance across time is critical. Hindcasting
uses a temporal out of sample validation to mimic how well a model would have
performed had it been run in the past. For example using occurance data from the
early 20th century to model distributions which are validated with late
20th century occurances. Dense timeseries, such as yearly observations, are
desirable to also evalulate the forecast horizon (see #6), but this is not
a strict requirement.
